%% Preface chapter
%% author Liu Peng

This document is my Master's thesis for \textit{Communications Engineering, majoring in
Networking} at Aalto University. All research and development of this thesis was
conducted at Tuxera Inc. in Helsinki from January 2013 to June 2014. Tuxera is a
high-tech startup that develops kernel-level file systems and multimedia solutions
for leading software, hardware and electronics companies.\\
\\
During this project, I worked together with my colleagues at Tuxera, starting
to work on the DLNA project in the first few months during which time I learned
DLNA architecture and conducted the research about Digital Media Server solutions.
After that, I worked on an Android project to develop a universal solution for
multimedia home networking.
\subsection*{Acknowledgements}
First of all, I would like to thank the Streambels team at Tuxera, with whom I worked
together throughout the project. I would like to thank Karthik Ramakrishna, our
lead developer. Every week, he helped solve problems in the project.
No matter whether the question was theoretical or technical, he always answered my
questions. As our project manager, Oscar Santolalla helped us with
the organizational problems that we encountered and taught us to look from the
end-user perspective as well. Sakari Tanskanen, our mobile developer helped us
by integrating Chromecast and FireTV support for Streambels. Nadir Javed, our
quality assurance engineer helped us with the quality management and testing of
potential bugs before releasing the product to end users. Karolina Mosiadz, our
Public Relations Manager listened to user feedback every day and provided the unique
insights to improve Streambels. Hien Le, our UX designer helped us to develop
a quite intuitive user interface. And special thanks to Mikko Valimaki and Szabolcs
Szakacsits who led the company and gave me the opportunity to participate in
this great project. Without them, I would not have been able to finish this
report.\\
\\
I thank my university supervisor Raimo Kantola, who helped me to develop a good
thesis topic based on my project and helped me with initial problem description.
I reveived great support from him with his constructive criticism and useful advice, especially
during the middle and final phase, when I wrote the report.\\
\\
Finally, I thank everybody who supported me during my graduate work,
especially my family, friends, and housemates.